Lens Modeling in \sw

### 2013-09-10 text/tex/results.tex
minor ajustments to plots and tables

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/006917/input.png}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/006917/spaghetti.png}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/ASW0001hpf/arriv.png}}
%  \subfigure{\includegraphics[width=0.45\textwidth]
%             {fig/sims/ASW0001hpf/extr_points.png}}
  \caption{Examples of Spaghetti input (left top) and modeled arrival time surface (right top) vs reconstructed arrival time surface from simulation parameters (bottom left), additionally using a extremal point detector (bottom right).}
  \label{fig:output_compare}
\end{figure}

@@

In \tabref{stats} a summary of this evaluation is presented.

@@

We conclude that the volunteers are performing very well identifying and positioning images (T1a), with a performance of 92\% (approxPlace p=0.92).
Most of the problems where due to unclear arc-like structures (Error 1, p=0.18; Error 4, p=0.03; Error 8, p=0.04).
Critical failures like the failure to identify all fife images in an fife image system (Error 3, p=0.04) or to include too many images (Error 10, p=0.01) did almost never happened.
From this we conclude that the introduction materials was adequate and the volunteers understand the basics of gravitational lensing.

@@

The assignment of the parity of the images (T1b) posed a more difficult task.
In 59\% (rightOrder, p=0.59, N=70) of the cases the volunteers succeeded to identify the right configuration.
Most of the failures are due to Error 6 (PI/2), with N=38, p=32\%, followed by Error 5 (PI) with N=7, p=6\%.
For an example of type 6 error, see \figref{6971}.
While these errors occurred, we suspect they can be avoided with better training material and some examples for the obvious cases.
For more challenging cases, like very symmetrical distribution of the lensed images (for example model 6971, \figref{6971}), those errors should still produce plausible results, as will be explained in the next section.

@@

To compare the enclosed mass profile and the Einstein radius of the simulation and the models, \kenc was calculated using the mass map \kap[x,y] directly generated in the modeling process.
From the ensemble of models generated by one modelling process, the mean is taken as the resulting $\kappa(r)$ to calculate $\theta_E$.
To estimate the errors, also the extremal models are used to estimate a lower and upper limit for $\theta_E$.
These results can be seen in \figref{eR_all_models}.
This figure shows that this tecnique of esitmating the error is underestimating the error significantly and should be improved for further analysis.

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/sims/eR_1.png}
  \caption{\tEr \gEr for all models with estimated erros in blue, \gEr of simulation in red}
  \label{fig:eR_all_models}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/sims/eR_4.png}
  \caption{relative Einstein Radius for each model, per sim. red crosses for models made by an expert.}
  \label{fig:eR_per_sim}
\end{figure}

@@

Two additional sims were modeled by an expert, \asw{1hpf} and \asw{0vqg}.
Looking at the results for \gEr for those models in \figref{eR_per_sim}, we conclude that the performance of volunteers (blue crosses) and experts (red crosses) is comparable.
Please note that the models of \asw{0vqg} with \gEr{, rel} around 0.25 (6935 -- 6937) are failed models that show the attempts of a single user, that came finally up with model 6938 as final result.\todo{remove?}

>>>>

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/006917/input.png}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/006917/spaghetti.png}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/ASW0001hpf/arriv.png}}
%  \subfigure{\includegraphics[width=0.45\textwidth]
%             {fig/sims/ASW0001hpf/extr_points.png}}
  \caption{Examples of Spaghetti input (left top) and modeled arrival time surface (right top) vs reconstructed arrival time surface from simulation parameters (bottom).}
  \label{fig:output_compare}
\end{figure}

@@

@@

In \tabref{stats} a summary of this evaluation is presented.
We conclude that the volunteers are performing very well identifying and positioning images (T1a), with a performance of 92\% (R1 p=0.92).
Most of the problems where due to unclear arc-like structures (E01, p=0.18; E04, p=0.03; E08, p=0.04).
Critical failures like the failure to identify all five images in an five image system (E03, p=0.04) or to include too many images (E10, p=0.01) did almost never happened.
From this we conclude that the introduction materials was adequate and the volunteers understand the basics of gravitational lensing.

@@

The assignment of the parity of the images (T1b) posed a more difficult task.
In 59\% (R2, p=0.59, N=70) of the cases the volunteers succeeded to identify the right configuration.
Most of the failures are due to E06, with N=38, p=32\%, followed by E05 (PI) with N=7, p=6\%.
For an example of E06, see \figref{6971}, it basically describes a situation, where the minima and saddlepoints were exchanged (rotated by $\pm90\dgr$).
E05 describes the situation, where the ordering of the saddle points was wrong (rotation by $180\dgr$)
While these errors occurred, we suspect they can be avoided with better training material and some examples for the obvious cases.
For more challenging cases, like very symmetrical distribution of the lensed images (for example model 6971, \figref{6971}), those errors should still produce plausible results, as will be explained in the next section.

@@

To compare the enclosed mass profile and the Einstein radius of the simulation and the models, \kenc was calculated using the mass map \kap[x,y] directly generated in the modeling process.
From the ensemble of models generated by one modeling process, the mean is taken as the resulting $\kappa(r)$ to calculate $\theta_E$.
To estimate the errors, also the extremal models are used to estimate a lower and upper limit for $\theta_E$.
These results can be seen in \figref{eR_all_models}.
This figure shows that this technique of estimating the error is underestimating the error significantly and should be improved for further analysis.

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/sims/eR_1.png}
  \caption{\tEr \gEr for all models with estimated errors in blue squares, \gEr of simulation in red crosses}
  \label{fig:eR_all_models}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/sims/eR_4.png}
  \caption{relative Einstein Radius \gEr / \gEr[, sim] for each model, per sim. red crosses with right offset for models made by an expert.}
  \label{fig:eR_per_sim}
\end{figure}

@@

Two additional sims were modeled by an expert, \asw{1hpf} and \asw{0vqg}.
Looking at the results for \gEr for those models in \figref{eR_per_sim}, we conclude that the performance of volunteers (blue crosses) and experts (red crosses, offset) is comparable.
Please note that the models of \asw{0vqg} with \gEr{, rel} around 0.25 (6935 -- 6937) are failed models that show the attempts of a single user, that came finally up with model 6938 as final result.\todo{remove?}
